Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages

### 2019-04-22 sattose/paper.tex
Working on sattose paper

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/CodeGraph}
  \caption{Graph representation built by CloneRefactor}
  \label{fig:clonerefactor}
\end{figure}

@@

\subsubsection{Third Level Heading}

Third level headings must be flush left, initial caps and bold.
One line space before the third level heading and $1/2$ line
space after the third level heading.

\paragraph{Fourth Level Heading}

Fourth level headings must be flush left, initial caps and roman type.
One line space before the fourth level heading and $1/2$ line
space after the fourth level heading.

\subsection{Citations In Text}

Citations within the text should indicate the author's last name and
year\cite{Knuth-vol3}. Reference style\cite{Comer-btree}
should follow the style that you are used to using, as long as the
citation style is consistent.

\subsubsection{Footnotes}

Indicate footnotes with a number\footnote{This is a sample footnote} in
the text. Place the footnotes at the bottom of the page they appear on.
Precede the footnote with a vertical rule of 2 inches (12 picas).

\subsubsection{Figures}

All artwork must be centered, neat, clean and legible. Do not use pencil
or hand-drawn artwork. Figure number and caption always appear after the
the figure. Place one line space before the figure, one line space
before the figure caption and one line space after the figure caption.
The figure caption is initial caps and each figure is numbered
consecutively.

Make sure that the figure caption does not get separated from the
figure. Leave extra white space at the bottom of the page to avoid
splitting the figure and figure caption.

Figure \ref{fig1} shows how to include a figure as encapsulated postscript.
The source of the figure is in file {\tt fig1.eps}.

Below is another figure using LaTeX commands.

\begin{figure}[ht]
\begin{center}
\setlength{\unitlength}{1pt}
\footnotesize
\begin{picture}(160,80)
        \put(0,0){\framebox(160,80)[]{}}
        \put(10,35){\framebox(80,40){}}
        \put(100,20){\framebox(40,20){}}
        \put(70,10){\framebox(20,10){}}
        \put(20,5){\framebox(10,5){}}
\end{picture}
\caption{Sample Figure Caption}
\end{center}
\end{figure}

>>>>

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/CodeGraph}
  \caption{Abstract figure of the graph representation built by CloneRefactor}
  \label{fig:clonerefactor}
\end{figure}

@@

As a result, we got the following table:
